Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-15 write-ups/PLDI/paper.tex
Added citation.

There are three main avenues for future work at present: seeking
additional classes of irregular algorithms to which the model might
(be extended to) apply (to), investigating native driver support for
cooperative kernels via open source graphics drivers, and integrating
cooperative kernels into template- and compiler-based programming
models for graph algorithms on
GPUs~\cite{SreesCompetition,DBLP:conf/oopsla/PaiP16}.  As more vendors
adopt the advanced features of OpenCL that our approach requires, we
will be in a position to assess the programming model across a wider
range of devices.

>>>>

There are three main avenues for future work at present: seeking
additional classes of irregular algorithms to which the model might
(be extended to) apply (to), investigating native driver support for
cooperative kernels via open source graphics drivers, and integrating
cooperative kernels into template- and compiler-based programming
models for graph algorithms on
GPUs~\cite{DBLP:conf/ppopp/WangDPWRO16,DBLP:conf/oopsla/PaiP16}.  As more vendors
adopt the advanced features of OpenCL that our approach requires, we
will be in a position to assess the programming model across a wider
range of devices.
